\papertitle

### 2021-03-03 source_separation/paper/paper.tex
Add to introduction

	\textit{The following is directly copy/pasted from our last paper, it will need to be changed in order to avoid self-plagiarism}

@@

	takes a target sound as an input and attempts to find instrumental samples that best match the target given a specific similarity metric and a set of constraints. A solution to this problem is a set of orchestral scores that represent the mixtures of audio samples in the database, ranked by similarity with the target sound.

@@

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, then calculates the spectral distance as defined in Eqn. \ref{eqn:distance} between corresponding frames. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} \textbf{(is it weird/bad to cite our last paper?)}to compare accuracies of orchestrations. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

	\section{Future Work}\label{sec:futurework}
	Implementing these methods in Orchidea. We could improve the supervised methods by training them ourselves with data that fits our problem better.

>>>>

	\textit{The following (from here until the line) is directly copy/pasted from our last paper, it will need to be changed in order to avoid self-plagiarism}

@@

@@

		Source separation is an important addition to improve orchestration as it allows for the orchestration of more complex sounds in a way that makes sense in an orchestral context. Orchestral music often uses multiple layers, so by separating the layers of a target and individually orchestrating them, the resulting solution is improved. \textbf{(@Carmine, can you make sure this paragraph makes sense/is correct?)}

		For example, consider an example target that has a continuous drone sound throughout and a bird song playing above this drone. Without source separation, Orchidea would detect each note of the bird song as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, forcing it to have a new onset each time the bird song changes notes. The resulting orchestration would having multiple onsets for the drone, when really only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and bird song would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset of note(s) that lasts for the duration of the drone. At the same time, the bird song could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we hope to achieve through implementing source separation in computer-assisted orchestration.

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, then calculates the spectral distance as defined in Eqn. \ref{eqn:distance} between corresponding frames. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} \textbf{(is it weird/bad to cite our last paper?)} to compare accuracies of orchestrations. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

	\section{Future Work}\label{sec:futurework}
	Implementing these methods in Orchidea. We could improve the supervised methods by training them ourselves with data that fits our problem better. Adding a joint optimization to determine which instruments should be used in which sources.
